Design Document for R Package glmm

### 2016-06-30 NewDesignDoc/DesignDocGLMM.tex
About to start implementing bin fam in glmm
Added a bit to pre-processsing, produce errors
Next, need to change pql to take in ntrials and it should be good.
adding mcse details to design doc

\item I will add checks for the model matrix stage.  See below.
\item I want to allow the response for bernoulli to be a single vector  (rather than two cbinded vectors). Therefore, if the family is binomial.glmm and the length of the dimension of the response is 1 (meaning we just have a vector), then create the ntrials vector to be a vector of 1s. Test this with salamanders or some other problem to make sure it gives the same results.

\end{enumerate}

Checks for the model matrix stage: 
\begin{enumerate}
\item  If  the length of the dimension of the response is 2 dimensions (meaning we have both rows and columns), then the family must be binomial.glmm.
\item If the family is binomial.glmm, then the response must have 2 columns
\end{enumerate}

@@

>>>>

\item I will add checks for the model matrix stage. 
\begin{enumerate}
\item  If  the length of the dimension of the response is 2 dimensions (meaning we have both rows and columns), then the family must be binomial.glmm.
\item If the family is binomial.glmm, then the response must have 2 columns
\end{enumerate}
\item I want to allow the response for bernoulli to be a single vector  (rather than two cbinded vectors). Therefore, if the family is binomial.glmm and the length of the dimension of the response is 1 (meaning we just have a vector), then create the ntrials vector to be a vector of 1s. Test this with salamanders or some other problem to make sure it gives the same results.
\item Change PQL function to do binomial.
\end{enumerate}

@@

\subsection{MCSE}
Let  $\gamma_1$ be defined as
\begin{align}
  \gamma_1 = \int  f_\theta(u,y) \; du =  f_\theta(y). \label{eq:gamma1} 
\end{align}
My thesis shows the Monte Carlo error of the gradient of the log likelihood at the MLE $\hat{\theta}$ is 
\begin{align}
V= \dfrac{1}{\gamma_1^2}  \int \left[  \nabla \log f_{\hat{\theta}}(u,y)  \right] \left[  \nabla \log f_{\hat{\theta}}(u,y)  \right]^T \dfrac{f_{\hat{\theta}}(u,y)^2}{\tilde{f}(u)} \, du.
\end{align}

We can estimate this with the MCMLE $\hat{\theta}_m$:
\begin{align}
\hat{V}= \dfrac{ \dfrac{1}{m}  \sum_{k=1}^m \left( \left[\nabla \log f_{\hat{\theta}_m}(u_k,y)  \right] \left[\nabla \log f_{\hat{\theta}_m}(u_k,y)  \right]^T  \dfrac{ f_{\hat{\theta}_m}(u_k,y)^2   }{\tilde{f}(u_k)}  \right) }
{  \left( \dfrac{1}{m} \sum_{k=1}^m  \dfrac{ f_{\hat{\theta}_m}(u_k,y)   }{\tilde{f}(u_k)} \right)^2 }_.
\end{align}
%\begin{align}
%\hat{V}= \dfrac{   \sum_{k=1}^m \left( \left[ \nabla \log f_{\hat{\theta}_m} (u_k,y)  - \nabla l_m({\hat{\theta}_m}|y)   \right] \left[ \nabla \log f_{\hat{\theta}_m}(u_k,y)  -\nabla l_m({\hat{\theta}_m}|y)  \right]^T  \dfrac{ f_{\hat{\theta}_m}(u_k,y)   }{\tilde{f}(u_k)}  \right) }{\sum_{k=1}^m  \dfrac{ f_{\hat{\theta}_m}(u_k,y)   }{\tilde{f}(u_k)}}_.
%\end{align}

Let U be the Hessian of the likelihood evaluated at the MLE. This is estimated by
\begin{align}
\hat{U} = \nabla^2 l_m (\hat{\theta}_m |y).
\end{align}
In other words, $\hat{U}$ is the  MCLA Hessian evaluated at the MCMLE.

Then the MCSE of $\hat{\theta}_m$ is the square root of the diagonal elements of
\begin{align} 
\dfrac{1}{m} \, \hat{U}^{-1} \, \hat{V} \, \hat{U}^{-1}
\end{align}
under the regularity conditions listed in \citet{geyer:1994}.

The breakdown for programming MCSE is:
\begin{enumerate}
\item Get $\hat{U}$ from output's \texttt{likelihood.hessian}
\item Stably invert $\hat{U}$
\item Calculate $\hat{V}$
\item Finish calculation (result will be a vector of MCSE with length equal to number of parameters)
\item Output table
\end{enumerate}
The output table will have a row for each parameter. The columns will be estimate (MCMLE), SE, MCSE. This will allow for easy comparison between SE and MCSE so that users can ensure their MCSE is small enough compared to the SE.

Note on calculating $\hat{U}$:the likelihood's Hessian is calculated for every call of objfunc. We can get this from the output's \texttt{likelihood.hessian}.

To do steps:
\begin{enumerate}
\item Remember how to do QR decomp (or some other stable matrix decomposition to stable invert the matrix)
\item Calculate $\hat{V}$ and the rest of the MCSE calculation in R
\item Change the  $\hat{V}$ calculation to C
\end{enumerate}

\subsection{Revisit Summary Table}
I just realized I have \texttt{solve()} for calculating the variance-covariance matrix. I need to do a QR decomposition or something more stable.
